A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation

### 2016-06-20 crystal-gel/talk_Roscoff.tex
Move "Another class of gel? Crystal-gel?" from intro to after crystal gel detected "Crystals outgrow metastable liquid" with graphs + experimental slices "Dynamics: Bergeron > Ostwald" with pathX scheme and triangle (redone in tikz)

	\only<3>{
	\nextgroupplot[
		title={cluster size distribution},
		xlabel={$s$}, ylabel={$R_g/\sigma$},
		xmin=1, xmax=4e3,
		ymin=0.5, ymax=30,
		xmode=log, ymode=log, 
		clip mode=individual,
		]
		\addplot file{data/fig1b_sqrt_1.dat};
		\addplot file{data/fig1b_sqrt_2.dat};
		\addplot file{data/fig1b_sqrt_3.dat};
		\addplot file{data/fig1b_sqrt_4.dat};
		\addplot file{data/fig1b_sqrt_5.dat};
		\addplot[gray, ultra thick, domain=1:4e3] {0.629*x^(1/2.53)} node [left] at (rel axis cs:1,0.9){$D=2.53$};
	}
	\only<4>{
	\nextgroupplot[
		title={structure factor},
		xlabel={$q\sigma$}, ylabel={$S(q)$},
		xmode=log, ymode=log, xmin=0.2, xmax=20, ymin=0.1,
		restrict x to domain=-1.8:3, unbounded coords=discard, 
		%clip mode=individual
		]
		\addplot+[clip mode=individual] file{data/fig3c_1.dat};
		\addplot+[clip mode=individual] file{data/fig3c_2.dat};
		\addplot file{data/fig3c_3.dat};
		\addplot+[clip mode=individual] file{data/fig3c_4.dat};
		\addplot+[clip mode=individual] file{data/fig3c_5.dat};
		\addplot[black, ultra thick, domain=0.1:3] {2.14605*x^(-3)} node[pos=0.92,left=0.5em] {$D=3$};
		\addplot[gray, ultra thick, domain=0.1:3] {3.98797*x^(-2.53)} node [pos=0.65, above right] {$D=2.53$};
	}
	\only<5>{
	\nextgroupplot[
		title={local volume fraction},
		xlabel={\# neighbours}, ylabel={$\phi$ [\%]},
		xmin=0, ymin=0, ytick={0,10,30,50},
		extra y ticks={64, 72}, extra y tick style={grid=major}, extra y tick label={},
		legend pos=north west, legend style={font=\footnotesize},
		no markers,
		/pgfplots/error bars/y dir=both, /pgfplots/error bars/y explicit,
		]
		\addplot table[y error=err]{data/vol_err_phi_0.10_cp_0.82.scaled};
		\addplot table[y error=err]{data/vol_err_phi_0.10_cp_1.36.scaled};
		\addplot table[y error=err]{data/vol_err_phi_0.25_cp_0.38.scaled};
		\addplot table[y error=err]{data/vol_err_phi_0.25_cp_0.48.scaled};
		\addplot table[y error=err]{data/vol_err_phi_0.25_cp_0.57.scaled};
	}

	\end{groupplot}
	\node[anchor=north west, rotate=90, inner xsep=0,lightgray] (x) at (g c1r1.south east) {crystal};
	%\draw(g c1r1.outer south west) -- +(\textwidth,0);
	\end{tikzpicture}
	\vspace{-0.5em}
	\begin{itemize}
	\item<2-> Good agreement with theoretical phase diagram
	\item<3-> At percolation time, compatible with random gelation
	\item<4-> Final stucture compatible with random gelation \alert{Except} \textcolor{red}{$\bullet$}
	\item<5-> Glassy local $\phi$ for 12-neighboured particles \alert{Except} \textcolor{red}{$\bullet$}
	\end{itemize}
\end{frame}

@@

\begin{frame}{Crystals outgrow liquid}
\vspace{\baselineskip}
\tikzsetnextfilename{crystal_fates}%
\begin{tikzpicture}
\begin{groupplot}[%
			group style={
				group name=g, group size=2 by 1,
				horizontal sep=4em,
				},
		width=0.5\linewidth,
		%height=0.5\linewidth,
	]
	\nextgroupplot[
		title={nuclei},
		xlabel={$t/10^3\tau_B$}, ylabel=\#,
		xmin=0, xmax=13.0, ymin=0,
		no marks,
		legend style={cells={anchor=base west}},
		]
	\addplot table[x expr={\thisrowno{0}/2.3e3}]{data/fig3a_1.dat} node[left] at (rel axis cs:1,0.2) {avg size};
	\addplot table[x expr={\thisrowno{0}/2.3e3}]{data/fig3a_2.dat} node[left] at (rel axis cs:1,0.6) {number};
	%\legend{average size, average number};

	\nextgroupplot[
		title={cluster size distribution},
		xlabel={$s$}, ylabel=$R_g/\sigma$,
		xmode=log, ymode=log,
		ytick={0.5, 1, 2, 4}, yticklabels={$\frac{1}{2}$, 1, 2, 4},
		domain=1:5e2,
		]
	\addplot[only marks, red, thick, mark=*] file{data/fig3d_sqrt_1.dat};
	\addplot[black, ultra thick] {0.522*x^(1/3)} node[below left] at (axis cs:9e2,2.5) {$D=3$};
	\addplot[gray, ultra thick] {0.426*x^(1/2.53)} node[pos=0.08,below right] {$D=2.53$};
\end{groupplot}
\end{tikzpicture}
\begin{center}
\tikzsetnextfilename{pathsX}\vspace{-0.5em}\input{presentation/pathsX.pgf}
\end{center}
\end{frame}

\begin{frame}{Dynamics: Bergeron > Ostwald}
\vspace{\baselineskip}
\includegraphics[width=\textwidth]{nature/fig4.pdf}
\end{frame}

>>>>

	\only<3>{
	\nextgroupplot[
		title={cluster size distribution},
		xlabel={$s$}, ylabel={$R_g/\sigma$},
		xmin=1, xmax=4e3,
		ymin=0.5, ymax=30,
		xmode=log, ymode=log, 
		clip mode=individual,
		]
		\addplot file{data/fig1b_sqrt_1.dat};
		\addplot file{data/fig1b_sqrt_2.dat};
		\addplot file{data/fig1b_sqrt_3.dat};
		\addplot file{data/fig1b_sqrt_4.dat};
		\addplot file{data/fig1b_sqrt_5.dat};
		\addplot[gray, ultra thick, domain=1:4e3] {0.629*x^(1/2.53)} node [left] at (rel axis cs:1,0.9){$D=2.53$};
	}
	\only<4>{
	\nextgroupplot[
		title={structure factor},
		xlabel={$q\sigma$}, ylabel={$S(q)$},
		xmode=log, ymode=log, xmin=0.2, xmax=20, ymin=0.1,
		restrict x to domain=-1.8:3, unbounded coords=discard, 
		%clip mode=individual
		]
		\addplot+[clip mode=individual] file{data/fig3c_1.dat};
		\addplot+[clip mode=individual] file{data/fig3c_2.dat};
		\addplot file{data/fig3c_3.dat};
		\addplot+[clip mode=individual] file{data/fig3c_4.dat};
		\addplot+[clip mode=individual] file{data/fig3c_5.dat};
		\addplot[black, ultra thick, domain=0.1:3] {2.14605*x^(-3)} node[pos=0.92,left=0.5em] {$D=3$};
		\addplot[gray, ultra thick, domain=0.1:3] {3.98797*x^(-2.53)} node [pos=0.65, above right] {$D=2.53$};
	}
	\only<5>{
	\nextgroupplot[
		title={local volume fraction},
		xlabel={\# neighbours}, ylabel={$\phi$ [\%]},
		xmin=0, ymin=0, ytick={0,10,30,50},
		extra y ticks={64, 72}, extra y tick style={grid=major}, extra y tick label={},
		no markers,
		/pgfplots/error bars/y dir=both, /pgfplots/error bars/y explicit,
		]
		\addplot table[y error=err]{data/vol_err_phi_0.10_cp_0.82.scaled};
		\addplot table[y error=err]{data/vol_err_phi_0.10_cp_1.36.scaled};
		\addplot table[y error=err]{data/vol_err_phi_0.25_cp_0.38.scaled};
		\addplot table[y error=err]{data/vol_err_phi_0.25_cp_0.48.scaled};
		\addplot table[y error=err]{data/vol_err_phi_0.25_cp_0.57.scaled};
	}
	\only<6>{
	\nextgroupplot[
		title={local $\phi$ 12-ngb particles},
		xlabel=$t/10^3\tau_B$, ylabel={$\phi$ [\%]},
		xmin=0,
		/pgfplots/error bars/y dir=both, /pgfplots/error bars/y explicit,
		]
		\addplot table[y error=err]{data/mediaphi_phi0.10_cp0.82.scaled};
		\addplot table[y error=err]{data/mediaphi_phi0.10_cp1.36.scaled};
		\addplot table[y error=err]{data/mediaphi_phi0.25_cp0.38.scaled};
		\addplot table[y error=err]{data/mediaphi_phi0.25_cp0.48.scaled};
		\addplot table[y error=err]{data/mediaphi_phi0.25_cp0.57.scaled};
	}
	\end{groupplot}
	\node[anchor=north west, rotate=90, inner xsep=0,lightgray] (x) at (g c1r1.south east) {crystal};
	\end{tikzpicture}
	\vspace{-0.5em}
	\begin{itemize}
	\item<2-> Good agreement with theoretical phase diagram
	\item<3-> At percolation time, compatible with random gelation
	\item<4-> Final stucture compatible with random gelation \alert{Except} \textcolor{red}{$\bullet$}
	\item<5-> Glassy local $\phi$ for 12-neighboured particles \alert{Except} \textcolor{red}{$\bullet$}
	\end{itemize}
\end{frame}

@@

\begin{frame}{Crystals outgrow metastable liquid}
	\vspace{\baselineskip}
	\tikzsetnextfilename{crystal_fates}%
	\begin{tikzpicture}
	\begin{groupplot}[%
				group style={
					group name=g, group size=2 by 1,
					horizontal sep=4em,
					},
			width=0.5\linewidth,
			%height=0.5\linewidth,
			xlabel absolute, every axis x label/.append style={anchor=base, font=\footnotesize, yshift=-0.5em},
		]
		\nextgroupplot[
			title={nuclei},
			xlabel={$t/10^3\tau_B$}, ylabel=\#,
			xmin=0, xmax=13.0, ymin=0,
			no marks,
			legend style={cells={anchor=base west}},
			]
		\addplot table[x expr={\thisrowno{0}/2.3e3}]{data/fig3a_1.dat} node[left] at (rel axis cs:1,0.2) {avg size};
		\addplot table[x expr={\thisrowno{0}/2.3e3}]{data/fig3a_2.dat} node[left] at (rel axis cs:1,0.6) {number};
		%\legend{average size, average number};

		\nextgroupplot[
			title={cluster size distribution},
			xlabel={$s$}, ylabel=$R_g/\sigma$,
			xmode=log, ymode=log,
			ytick={0.5, 1, 2, 4}, yticklabels={$\frac{1}{2}$, 1, 2, 4},
			domain=1:5e2,
			]
		\addplot[only marks, red, thick, mark=*] file{data/fig3d_sqrt_1.dat};
		\addplot[black, ultra thick] {0.522*x^(1/3)} node[below left] at (axis cs:9e2,2.5) {$D=3$};
		\addplot[gray, ultra thick] {0.426*x^(1/2.53)} node[pos=0.08,below right] {$D=2.53$};
	\end{groupplot}
	\end{tikzpicture}

	\hfill\includegraphics[width=0.95\textwidth, clip=true, trim=0 20cm 0 0]{nature/fig4.pdf}\hfill
\end{frame}

\begin{frame}{Dynamics: Bergeron > Ostwald}
	\vspace{\baselineskip}
	\begin{center}
	\tikzsetnextfilename{pathsX}\vspace{-0.5em}\input{presentation/pathsX.pgf}
	\end{center}
	\begin{columns}
	\column{0.5\textwidth}
	\begin{itemize}
	\item Individual trajectories
	\item Probability of path to X
	\end{itemize}
	\column{0.5\textwidth}
	\tikzsetnextfilename{pathsX2}%
	\begin{tikzpicture}
	\node[regular polygon, regular polygon sides=3, minimum width=5em] (tri){};
	\node[circle, minimum width=3.5em, fill=green!40, left=1em of tri.corner 2] (gas) {gas};
	\node[circle, minimum width=3.5em, draw, fill=white, right =1em of tri.corner 3] (liq) {liquid};
	\node[regular polygon, regular polygon sides=6, fill=red,minimum width=3.5em, inner sep=0, above=0 of tri.corner 1] (X) {crystal};
	\draw[->, very thick] ($(tri.corner 2)+(0,0.25em)$) -- ($(liq.west)+(0,0.25em)$) node[midway, above]{54\%}-- (X);
	\draw[->, very thick, dotted] ($(tri.corner 3)+(0,-0.25em)$) -- ($(gas.east)+(0,-0.25em)$) node[midway, below]{35\%}-- (X);
	\draw[->, very thick, dashed] (X) edge [in=190,out=-130,loop] node[left]{11\%} ();
	\end{tikzpicture}
	\end{columns}
\end{frame}
